---
title: "Untitled"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

library(rvest)

library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

```{r}
homicides_df = read.csv("data/homicide-data.csv")
```


# Problem 2
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help






Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}

all_df = 
  tibble(
    files = list.files(path="data/longitudinal_study"),
    path = str_c("data/longitudinal_study/", files)
  ) %>% 
  mutate(data = map(path, read_csv))%>% 
  unnest(data)


tidy_df=
  all_df %>% 
    select(-path) %>% 
    mutate(files=str_replace(files,".csv","")) %>% 
    separate(files,into=c("group","ID"),sep="_") %>% 
    mutate(group=str_replace(group,"con","control")) %>% 
    mutate(group=str_replace(group,"exp","experiment")) %>% 
    pivot_longer(
      week_1:week_8,
      names_to = "week",
      values_to ="outcome"
    ) %>% 
    mutate(week=str_replace(week,"week_",""),files=str_c(group,ID),ID=as.numeric(ID),week=as.numeric(week)) %>% 
    rename(subjects=files)%>% 
    select(subjects,everything())

tidy_df%>% 
  ggplot(aes(x=week,y=outcome)) + geom_line(aes(color=subjects)) + facet_grid(~group)
```

As shown in the plot,in the control group,the outcome of 10 subjects do not change a lot after 8 weeks.However,the outcome of 10 subjects in the experiment group increase in a roughly simple linear way.

## Problem 3

There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r}

set.seed(10)

iris_with_missing = iris %>% 
    janitor::clean_names() %>% 
    map_df(~replace(.x, sample(1:150, 20), NA)) %>%
    mutate(species = as.character(species))


fill_missing=function(x){
    if(!is.vector(x)){
      stop("argument should be a vector")
    }
    replace_na(x,"virginica")
    replace_na(x,mean(x,na.rm=TRUE))
}


iris_with_missing %>% 
  mutate(replace_na(mean(sepal_length,na.rm=TRUE)))


mean(iris_with_missing$sepal_length,na.rm=TRUE)


output=vector("list",length=5)
for (i in 1:5){
output[i]=map(iris_with_missing[i],fill_missing)
}



a=c(1,2,3,4,5,NA)
mean(a)
fill_missing(a)


```

